|

### 2021-09-29 article/articleCustomerDropoutMembership.Rmd
up

---
title: |
  |
  |
  |
  | \vspace{1cm}Customer dropout membership^[Corresponding address: sobreiro@esdrm.ipsantarem.pt. Quality of Life Research Centre, Polytechnic Institute of Santarém, Portugal]\vspace{0.5cm}
author: |
  | Pedro Sobreiro, Javier Berrocal, Domingos Martinho, José Garcia Alonso
  |
  | Extremadura University
  |
date: |
  |
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}Abstract of the article. Here we can place more info.\vspace{.8cm}
bibliography: refMembership.bib
csl: american-sociological-association.csl
output:
  bookdown::word_document2:
    latex_engine: xelatex
    number_sections: true
  bookdown::pdf_document2:
    includes:
    toc: no
    keep_tex: true
    latex_engine: xelatex
    number_sections: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin = 1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
   - \usepackage{pdfpages}
   - \usepackage{amsmath}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{hyperref}
editor_options: 
  markdown: 
    wrap: 80
---

@@

```{python createModel, eval=TRUE, echo=FALSE, cache = FALSE, warning = FALSE}
from pysurvival.models.survival_forest import RandomSurvivalForestModel
from sklearn.model_selection import train_test_split
from pysurvival.utils.metrics import concordance_index
from pysurvival.utils.display import integrated_brier_score
from pysurvival.utils.display import compare_to_actual

@@

cluster.fit(df_members)
df_members['cluster']=cluster.predict(df_members)
print(df_members.cluster.value_counts())
```

@@

fig, ax = plt.subplots()
for cluster in df_members.cluster.unique():
    x = df_members['X_pca'].loc[df_members.cluster == cluster]
    y = df_members['Y_pca'].loc[df_members.cluster == cluster]
    ax.scatter(x, y, label=cluster, alpha=1, edgecolors='none')

@@

    results = compare_to_actual(csf, X_test, t_test, e_test, is_at_risk = False,  
                                figure_size=(12, 6), metrics = ['rmse', 'mean', 'median'])
    print(results)

@@

In this section, we present our experiments to validate the proposed models,
comparing against other approaches. The models where optimized using the
hyper-parameters Grid Search technique. The explored hyper-parameters and the
best values of these parameters for every model are listed in (ref:table1).

(ref:table1) Table 2

```{=latex}
\begin{table}[ht]
    \footnotesize
    \centering
    \begin{tabular}{p{0.15\textwidth}p{0.55\textwidth}p{0.25\textwidth}}
    \hline
    \textbf{Model name} & \textbf{Explored parameters values} & \textbf{Best parameters} \\
    \hline
    Survival trees  & pysurvival random forest                  & a \\
    Survival trees
    with clusters   & pysurvival random forest with clusters    & a \\
    Scikit survival 
    trees           & scikit survival                           & a \\
    Scikit survival 
    with clusters   & scikit with clusters                      & a \\
    Scikit survival 
    gradient boost  & scikit survival gradient boost            & a \\
    Scikit survival 
    gradient boost 
    with clusters   & scikit with clusters                      & a \\
    \hline
    \end{tabular}
    \caption{Hyper-parameters best values}
    \label{hyperparametersbestvalues}
\end{table}
```
```{=html}
<!--
|        Model name        | Explored hyper-parameters' values                    | Best parameters |
| ------------------------ | ---------------------------------------------------- | --------------- |
| Survival trees           |                                                      |                 |   
| without cluster          |                                                      |                 |  
-->
```
# Conclusion

>>>>

---
title: |
  |
  |
  |
  | \vspace{1cm}Customer dropout membership^[Corresponding address: sobreiro@esdrm.ipsantarem.pt. Quality of Life Research Centre, Polytechnic Institute of Santarém, Portugal]\vspace{0.5cm}
author: |
  | Pedro Sobreiro, Javier Berrocal, Domingos Martinho, José Garcia Alonso
  |
  | Extremadura University
  |
date: |
  |
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}Abstract of the article. Here we can place more info.\vspace{.8cm}
bibliography: refMembership.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    includes:
    toc: no
    keep_tex: true
    latex_engine: xelatex
    number_sections: true
  bookdown::word_document2:
    latex_engine: xelatex
    number_sections: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin = 1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
   - \usepackage{pdfpages}
   - \usepackage{amsmath}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{hyperref}
editor_options: 
  markdown: 
    wrap: 80
---

@@

```{python createModel, eval=FALSE, echo=FALSE, cache = FALSE, warning = FALSE}
from pysurvival.models.survival_forest import RandomSurvivalForestModel
from sklearn.model_selection import train_test_split
from pysurvival.utils.metrics import concordance_index
from pysurvival.utils.display import integrated_brier_score
from pysurvival.utils.display import compare_to_actual

@@

cluster.fit(df_members)
df_members['cluster']=cluster.predict(df_members)
print(df_members.cluster.value_counts());
```

@@

fig, ax = plt.subplots()
for cluster in df_members.cluster.unique():
    x = df_members['X_pca'].loc[df_members.cluster == cluster]
    y = df_members['Y_pca'].loc[df_members.cluster == cluster]
    ax.scatter(x, y, label=cluster, alpha=1, edgecolors='none');

@@

    results = compare_to_actual(csf, X_test, t_test, e_test, is_at_risk = False,  
                                figure_size=(12, 6), metrics = ['rmse', 'mean', 'median'])
    print(f"Cluster {cluster} RMSE {results['root_mean_squared_error']}")
    print(f"Cluster {cluster} MAE {results['median_absolute_error']}")
    print(f"Cluster {cluster} MAError {results['mean_absolute_error']}")
```

@@

In this section, we present our experiments to validate the proposed models,
comparing against other approaches. The models where optimized using the
hyper-parameters Grid Search technique. The explored hyper-parameters and the
best values of these parameters for every model are listed in (Table 3).

```{=latex}
\begin{table}[ht]
    \footnotesize
    \centering
    \begin{tabular}{p{0.15\textwidth}p{0.55\textwidth}p{0.25\textwidth}}
    \hline
    \textbf{Model name} & \textbf{Explored parameters values} & \textbf{Best parameters} \\
    \hline
    Survival trees  & pysurvival random forest                  & a \\
    Survival trees
    with clusters   & pysurvival random forest with clusters    & a \\
    Scikit survival 
    trees           & scikit survival                           & a \\
    Scikit survival 
    with clusters   & scikit with clusters                      & a \\
    Scikit survival 
    gradient boost  & scikit survival gradient boost            & a \\
    Scikit survival 
    gradient boost 
    with clusters   & scikit with clusters                      & a \\
    \hline
    \end{tabular}
    \caption{Hyper-parameters best values}
    \label{hyperparametersbestvalues}
\end{table}
```
```{=html}
<!--
|        Model name        | Explored hyper-parameters' values                    | Best parameters |
| ------------------------ | ---------------------------------------------------- | --------------- |
| Survival trees           |                                                      |                 |   
| without cluster          |                                                      |                 |  
-->
```

The results of the performance of the models are available in table 4.
Colocar o modelo. Resultados do modelo
```{=latex}
\begin{table}[ht]
    \footnotesize
    \centering
    \begin{tabular}{p{0.15\textwidth}p{0.55\textwidth}p{0.25\textwidth}}
    \hline
    \textbf{Model name} & \textbf{Results} \\
    \hline
    Survival trees  & RMSE 2.77 Median Absolute Error 0.0 \\
    Survival trees
    with clusters   & Cluster 1: RMSE  2.775 Median Absolute Error  0.000 
                      Cluster 3: RMSE  8.769 Median Absolute Error  1.276
                      Cluster 2: RMSE 14.883 Median Absolute Error  2.030
                      Cluster 4: RMSE  9.624 Median Absolute Error  4.748
                      Cluster 0: RMSE 77.236 Median Absolute Error 26.066 \\
    Scikit survival 
    trees           & scikit survival                           \\
    Scikit survival 
    with clusters   & scikit with clusters                      \\
    Scikit survival 
    gradient boost  & scikit survival gradient boost           \\
    Scikit survival 
    gradient boost 
    with clusters   & scikit with clusters                      \\
    \hline
    \end{tabular}
    \caption{Hyper-parameters best values}
    \label{hyperparametersbestvalues}
\end{table}
```
# Conclusion
